Multilevel computation of glacier geometry \\ from Stokes dynamics

### 2021-05-26 paper/msg.tex
This figure shows how I imagine the extruded mesh will be used.

All FE computations in this paper use the Python library Firedrake \cite{Rathgeberetal2016}, which applies an embedded domain language \cite{Alnaesetal2014} to convert weak forms into discrete equations which are solved in parallel using the PETSc \cite{Balayetal2020} library.  For $s^h \in \mathcal{K}^h$ we will compute $\Phi^h(s^h)$, namely the numerical Glen-Stokes \eqref{eq:glenstokesweak} surface velocity associated to the surface elevation $s^h$, using a extruded-mesh approximation of $\Lambda_s^h \subset \RR^{d+1}$, the icy domain as defined by \eqref{eq:lambdas}.  Specifically, if $d=2$ and if $\mathcal{T}$ is a triangulation of $\Omega \subset \RR^d$, and given $s^h$ and $b^h$ from $\mathcal{V}^h$, we apply the Firedrake concept of an extruded mesh \cite{Gibsonetal2019,McRaeetal2016} to give a prism element decomposition of $\Lambda_s^h$.  If $d=1$ then the extruded mesh has quadrilateral elements; a sketch is shown in Figure \ref{fig:extruded}.

\begin{figure}[t]
\begin{center}
FIXME %\includegraphics[width=\textwidth]{genfigs/extruded.pdf}
\end{center}
\caption{Given a triangulation ($d=2$) or interval decomposition ($d=1$ as shown) of $\Omega$, to compute $\Phi^h(s^h)$ for $s^h \in \mathcal{K}^h$ we use a Firedrake extruded mesh of prisms or quadrilateral, respectively, to discretize $\Lambda_s^h$.}
\label{fig:extruded}
\end{figure}

>>>>

All FE computations in this paper use the Python library Firedrake \cite{Rathgeberetal2016}, which applies an embedded domain language \cite{Alnaesetal2014} to convert weak forms into discrete equations which are solved in parallel using the PETSc \cite{Balayetal2020} library.  For $s^h \in \mathcal{K}^h$ we will compute $\Phi^h(s^h)$, namely the numerical Glen-Stokes \eqref{eq:glenstokesweak} surface velocity associated to the surface elevation $s^h$, using a extruded-mesh approximation of $\Lambda_s^h \subset \RR^{d+1}$, the icy domain as defined by \eqref{eq:lambdas}.  Specifically, if $d=2$ and if $\mathcal{T}$ is a triangulation of $\Omega \subset \RR^d$, and given $s^h$ and $b^h$ from $\mathcal{V}^h$, we apply the Firedrake concept of an extruded mesh \cite{McRaeetal2016} to give a prism element decomposition of $\Lambda_s^h$.  If $d=1$ then the extruded mesh has quadrilateral elements; a sketch is shown in Figure \ref{fig:extruded}.

\begin{figure}[t]
\begin{center}
\includegraphics[width=\textwidth]{genfigs/extruded.pdf}
\end{center}
\caption{We compute $\Phi^h(s^h)$ by solving \eqref{eq:glenstokesweak} on an extruded mesh.  In the ``pinched'' extrusion (left), $s^h$ defines where the trace of $\bu^h$ is evaluated (strong).  In the ``cliffs'' extrusion (right) all elements have a minimum thickness $H_{\text{min}} / m_z$, so the trace evaluation may be above the original $s^h$ (dotted).}
\label{fig:extruded}
\end{figure}
